Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-01 ms.tex
brak2

This appears to be in contradiction with the general down sizing trend observed for SMBH accretion in the local universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08})

Our analytic expression for the accretion rate (eq.~[\ref{eq:mdot_analytic}]) can be translated into the growth time of the SMBH $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$,
\begin{eqnarray}
  t_{\rm growth}/t_{\rm h} \approx 
  \begin{cases}
    250 M_{\bullet,8}^{-0.76}
    v_{500}^{3.8}   \eta_{0.02}  & \text{core} \\
    140 \Mbheight^{-0.48}
    v_{500}^{2.4}   \eta_{0.02}  & \text{cusp}, 
  \end{cases}
  \label{eq:tgrow_analytic}
\end{eqnarray}
which we have normalized in terms of the Hubble time.

There is a maximum accretion rate for a thermally stable flow
(eqn. [\ref{eq:Mdotmax}]). This gives a lower bound on the growth
time from thermally stable accretion

\begin{align}
  t_{\rm growth}/t_{\rm h} \gsim
  \rm{max}\begin{cases}
    9 \eta_{0.02}^{-0.47} \Mbh^{-0.34} &, \text{core}\\
    15 \eta_{0.02}^{-0.59} \Mbh^{-0.29} &, \text{cusp}\\
    50  \eta_{0.02}^{-1} &, v_{\rm TI} < \sigma
  \end{cases}
  \label{eq:tgrow_min}
\end{align}

In Figure~\ref{fig:bh_growth} we plot the growth times for core and
cusp galaxies, with parameters chosen for the average star formation
history at each $\Mbh$ (see Figure~\ref{fig:vwSources}
and~\ref{fig:eta}). Core and cusp galaxies are shown in green and blue
respectively.  We also plot the maximum growth time for thermal
instability from equation~\eqref{eq:tgrow_min} in purple.

@@

Our results on SMBH accretion rates.

Plot showing final lorentz factor after the reverse shock crossing as a function of BH mass, using average star formation history.  place J1644+57 on the plot.

>>>>

The bottom panel of Figure~\ref{fig:bh_growth} shows the growth times for core and cusp galaxies, with parameters chosen for the average star formation history at each $\Mbh$ (see Figure~\ref{fig:vwSources} and~\ref{fig:eta}). Core and cusp galaxies are shown in green and blue respectively.  We also plot the maximum growth time for thermal
instability from equation~\eqref{eq:tgrow_min} in purple.

@@

Our results also have implications for jetted TDEs.  For black hole masses characterizing those responsible for {\it Swift} J1644+57, we predict accretion rates of $\dot{M} \sim$ corresponding to gas densities of $n \sim 0.1$ cm$^{-3}$ on radial scales.  This is similar to the value of $n \sim 1$ cm$^{-3}$ inferred for J1644+57 on radial scales $\sim 0.3$ pc (\citealt{Metzger+12}, \citealt{Berger+12}).
